curatedMetagenomicData

### 2019-10-04 curatedMetagenomic_NS.Rmd
updated

@@

loman.filt = subset_taxa(fpseq, keepotu & !is.na(Strain))
plot_heatmap(fpseq, method="PCoA", distance="bray")

@@

>>>>

wt = UniFrac(pseq.csubset, weighted=TRUE, normalized=FALSE, 
             parallel=FALSE, fast=TRUE)
plot(hclust(wt), main="Weighted UniFrac distances")

@@

# This doesnt run. 
# plot_heatmap(fpseq, method="PCoA", distance="bray")

@@

barplot(sort(taxa_sums(pseq.csubset), TRUE)[1:20] / nsamples(pseq.csubset),
        ylab = "Total counts", las = 2)
